Lesson 5
========================================================



```{r Third Qualitative Variable}
library(ggplot2)
library(dplyr)
pf <- read.csv('~/R/sv_files/pseudo_facebook.tsv', sep = '\t')

ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot() + 
  stat_summary(fun.y = mean, geom = 'point', shape = 4) + 
  coord_cartesian(ylim = c(10, 60))

ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(gender))) + 
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)


pf.fc_by_age_gender <- pf %>%
  na.omit() %>%
  group_by(age, gender) %>%
  summarize(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n())
head(pf.fc_by_age_gender)
```

***


```{r Plotting Conditional Summaries}
ggplot(data = pf.fc_by_age_gender,
       aes(x = age, y = median_friend_count)) + 
  geom_line(aes(color = gender))
```

***


```{r}
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(x = age, y = female/male), 
       data = pf.fc_by_age_gender.wide) + 
  geom_line() + 
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
names(pf)
pf$year_joined <- 2014 - floor(pf$tenure/365)
rnorm(pf$age)

```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
summary(pf$year_joined)
table(pf$year_joined)
?cut
pf$year_joined.bucket <- cut(pf$year_joined, c(2004, 2009, 2011, 2012, 2014))
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(pf$year_joined.bucket, useNA = 'ifany')

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = mean) +
  geom_line(aes(x = age, y = friend_count), data = pf,
            stat = 'summary', fun.y = mean, linetype = 2)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(pf, tenure > 1), summary(friend_count/tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?
0.2204

What is the maximum friend rate?
417.0000 

```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated/tenure), 
       data = subset(pf, tenure > 1)) + 
  geom_line(aes(color = year_joined.bucket), 
            stat = 'summary', fun.y = mean)
```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) + 
  geom_smooth(aes(color = year_joined.bucket))

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

```{r Histograms Revisited}
yogurt <- read.csv('~/R/sv_files/yogurt.csv')
yogurt$id <- factor(yogurt$id)

str(yogurt)

sd(yogurt$price)

ggplot(aes(x = price), data = yogurt) + 
  geom_histogram(binwidth = 5, fill = 'orange')
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
str(yogurt)
yogurt$all.purchases <- (yogurt$strawberry + yogurt$blueberry + yogurt$pina.colada +
                           yogurt$plain + yogurt$mixed.berry)
```

***

### Prices over Time
Notes:

```{r Prices over Time}

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

