Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv('sv_files/pseudo_facebook.tsv', sep = '\t')

qplot(x = age, y = friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response:
There are more people in their 20's with higher friend counts. Also a one line that seems to go rather high, around late 60's to early 70s and two more distinct high lines slightly past the 100's
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20) + 
  xlim(13, 90)

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
age_friend_plot <- ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) + 
  xlim(13, 90)

age_friend_plot
```

#### What do you notice in the plot?
Response:
It does seem like there amounts I notice before are still there with the straight lines in the younger section and the one line in the late 60s. There's also a minor dip that happens in the 40s, and then it starts to drop off rather dramatically once you get older than 75.
***

### Coord_trans()
Notes:

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf, binwidth = 0.5) + 
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) + 
  xlim(13, 90) + coord_trans(y = 'sqrt')
```

#### What do you notice?
At the younger ages friend count is solid below 1000 pretty much, however the older you get the more it seems to lift off to a point between 100-200.
***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_point(alpha = 1/15, position = position_jitter(h = 0)) + 
  xlim(13, 90) + 
  coord_trans(y = 'sqrt')
```

***


### Conditional Means

```{r Conditional Means}
install.packages('dplyr')
library(dplyr)

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups, 
                          friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n())

pf.fc_by_age <- arrange(pf.fc_by_age)
head(pf.fc_by_age)
```

### Conditional Means Alt Code

```{r Conditional Means Alt}
pf.fc_by_age_alt <- pf %>%
  group_by(age) %>%
  summarize(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)

head(pf.fc_by_age_alt)
```


Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) + 
  geom_line()
ggsave('plots/age_fc_mean_line.png')

ggplot(aes(x = age, y = friend_count_median), data = pf.fc_by_age) + 
  geom_line()
ggsave('plots/age_fc_median_line.png')
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_point(alpha = 1/15, position = position_jitter(h = 0),
             color = "orange") + 
  labs(title = 'Friendships Initiated by Age', x = "Person's Age",
       y = "Number of Friendships Initiated") + 
  coord_trans(y = 'sqrt') + 
  geom_line(stat = 'summary', fun.y = mean) + 
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .1),
            linetype = 2, color = 'blue') + 
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .5),
            linetype = 2, color = 'green') + 
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .9),
            linetype = 2, color = 'purple') + 
  coord_cartesian(xlim = c(13, 90), ylim = c(0, 500))

ggsave('plots/age_fic_overlap.png')
```

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$age, pf$friend_count, method = 'pearson')

with(pf, cor.test(age, friend_count, method = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:
-0.027
***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```

***


## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = 'orange') + 
  xlim(0, quantile(pf$www_likes_received, .95)) + 
  ylim(0, quantile(pf$likes_received, .95)) + 
  geom_smooth(method = 'lm', color = 'blue')

with(pf, cor.test(www_likes_received, likes_received))
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

